%-------------------------
% Resume in Latex
% Author : Sampath, Yelchuri
% License : Bowling Green State University
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Sampath Yelchuri}} & Email : \href{mailto:yvenkat@bgsu.edu}{yvenkat@bgsu.edu}\\
  \href{https://www.linkedin.com/in/sampath-yelchuri/}{Linkedin --}
  \href{https://github.com/sampathy}{GitHub --}
  \href{https://github.com/sampathy}{Academic Research}& Mobile : +1-628-777-8882 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bowling Green State University}{Bowling Green, OH}
      {Master of Science in Computer Science;  GPA: 4.0}{Aug. 2018 -- Aug. 2020}
    \resumeSubheading
      {Jawaharlal Nehru Tehnological Institute (JNTUH)}{Telangana, India}
      {Bachelor of Engineering in Computer Science and Engineering;  GPA: 3.7 (8.37/10.0)}{Sep. 2013 -- May. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Idaptive, LLC.}{Santa Clara, CA}
      {Software Engineering Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{}
          {Worked in Apps Development Team to design basic py-tests for several APIs or repositories in the GitHub.}
        \resumeItem{}
          {Exposure of working with several teams in Agile Scrum Methodology and re-branding information.}
        \resumeItem{}
          {Knowledge and experience of configuring SAML and OAuth Client 2.0 applications and testing various endpoint URLs using the postman tool.}
        \resumeItem{}
          {Hands-on experience working with various tools like Py-Charm, Visual Studio 2019, and Postman.}
      \resumeItemListEnd


    \resumeSubheading
      {Bowling Green State University}{Bowling Green, OH}
      {Graduate Research Assistant}{Jan 2019 - May 2019}
      \resumeItemListStart
        \resumeItem{}
          {Worked with the Life Sciences Department in support with designing several scripts and macros in java for image processing.}
        \resumeItem{}
          {Knowledge on several digital image processing techniques like Fast Fourier Transformation (FFT), Inverse Fast Fourier Transformation (Inverse-FFT), Image Filtering, and Morphological Operations.}
        \resumeItem{}
          {Hands-on experience working with Java Scripts, Macros, and ImageJ tool.}
      \resumeItemListEnd

    \resumeSubheading
      {UnitedHealth Group}{Telangana, India}
      {Associate Software Engineer}{Jul 2017 - Aug 2018}
      \resumeItemListStart
        \resumeItem{}
          {Experienced in designing and developing reports and dashboards for various line-of-businesses such as Medicaid, Medicare and Tricare.}
        \resumeItem{}
          {Worked on claims and clinical data of various applications like Integrated Clinical User Experience (ICUE), CareOne, Alturista, and FACETS.}
        \resumeItem{}
          {\textbf{Best Innovator Award - 2017} for automating a manual process using Automation Anywhere 9.0.}
        \resumeItem{}
          {Hands on experience working in designing simple ETL jobs using Petaho Business Analytics and Talend Open Studio.}
        \resumeItem{}
          {Used several tools likes Tableau, SAP Crystal Reports, PL/SQL Developer, Microsoft SQL Server, and Automation Anywhere9.0.}
      \resumeItemListEnd

    \resumeSubheading
      {DevmenIT}{Telangana, India}
      {Software Developer Intern}{May 2016 - Aug 2016}
      \resumeItemListStart
        \resumeItem{}
          {Focused on designing and developing Web Application that helps in locating the nearest blood donors in and around the victim's location.}
        \resumeItem{}
          {Hand-on experience on using Microsoft Visual Studio 2016, ASP.NET, and Microsoft SQL Server 2016.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Smart Cars - IOT, 5G, and MEC}: }
      {Working on designing  architectures for Internal and External Communication of Smart Cars and  focusing on simulating Smart Cars Communications with IoT, 5G and Mobile Edge Computing (MEC) using Vehicular Ad-hoc Networks (VANETs) and Oment++.}
    \resumeSubItem{\href{https://github.com/sampathy/Predicting-Hard-Drive-Failures-using-Machine-Learning}{\textbf{Predicting Hard-Drive Failures using Machine Learning}: }}
      {Worked on improving the accuracy of a model as part of predicting failures of hard-drives by applying different re-sampling techniques such as SMOTE, Under Sampling and Over Sampling techniques.}
    \resumeSubItem{\href{https://github.com/sampathy/Eradication-of-Accidents-using-Sensing-Technology-EAST-}{\textbf{Eradication of Accidents using Sensing Technology (EAST)}}: }
      {This project focuses on reducing accidents at steep curves using Intelligent Transportation Systems that covers a wide range of applications that include communication system, positioning, and sensing with help of Arduino and Ultra-Sonic sensors.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C, Java, SQL, Python, HTML, CSS, Javascript}
      \hfill
      \textbf{Tools}{: Postman, Anaconda, GitHub/GitLab.}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
